---
title: "mini-review"
author: "Yingjie"
date: "2023-03-29"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# To clear your environment
remove(list = ls())

## Load common packages and directories
getwd()
# library(here)
# here()
# set_here()

## Additional packages
library(tidyverse)
library(splitstackshape) ## `cSplit()`
library(Hmisc)
today <- format(Sys.time(), "%Y%m%d"); today ## "%Y%m%d%H%M"

dir.raw <- "./data/"
dir.fig <- "./figures/"
```



# Data import

## Load data
```{r include=FALSE}
getwd()

fs <- list.files(path = dir.raw, full.names = T, pattern = '.csv$'); fs
# csv <- "review_299449_20230330063918.csv"
csv <- fs[1]


dfs <- data.frame()

for (csv in fs) {
  
  # time <- basename(csv) %>% gsub('review_299449_', '', .) %>%
  #   str_sub(start = 1, end = 8)  %>%
  #   as.Date(., format = "%Y%m%d")
  # time
  
  t <- basename(csv) %>% gsub('review_299449_', '', .) %>%
    str_sub(start = 1, end = 14)  %>%
    as.POSIXct(.,format="%Y%m%d%H%M%S") 
  t
  
  d <- readr::read_csv(file = csv) %>%
    dplyr::mutate(date = t)
  
  dfs <- rbind(dfs, d)
  
}


dt_tracking <- dfs %>%
  dplyr::rename('id' = 'Covidence #') %>%
  dplyr::rename(Reviewer = `Reviewer Name`) %>%
  dplyr::rename("Levels" = "Organizational levels of analysis",
                'Type' = 'Flow Type') 



## load most updated data only 
f <- fs[length(fs)]; f
t <- basename(f) %>% gsub('review_299449_', '', .) %>%
    str_sub(start = 1, end = 14)  %>%
    as.POSIXct(.,format="%Y%m%d%H%M%S") 
t

dt <- readr::read_csv(file = f) %>%
  dplyr::mutate(date = t) %>%
  dplyr::rename('id' = 'Covidence #') %>%
  dplyr::rename(Reviewer = `Reviewer Name`) %>%
  dplyr::rename("Levels" = "Organizational levels of analysis",
                'Type' = 'Flow Type') 
```


```{r - progress}
dt_tracking %>%
  ### - keep old data and remove data in newest dates
  # arrange(desc(date)) %>%
  dplyr::distinct(id, Reviewer, .keep_all = T) %>%
  group_by(Reviewer, date) %>%
  tally() %>%
  add_count(Reviewer, wt = n, name = 'n_total') %>%
  # dplyr::mutate(date = as.Date(date)) %>%
  ggplot(aes(x = reorder(Reviewer, n_total), y = n, fill = date)) +
  geom_col(show.legend = F) +
  geom_text(aes(label = n), 
            # vjust = 0.5, hjust = 0, 
            position = position_stack(vjust = 0.5),
            color = 'gray90') +
  
  geom_text(
    aes(label = after_stat(y), group = Reviewer), 
    stat = 'summary', fun = sum, vjust = .5, hjust = 0, color = 'red', fontface = 'bold', size = 5
  ) +

  xlab('') +
  coord_flip() +
  theme_bw()
```





```{r - check consensus}

dt_check <- dt %>%
  arrange(id, Reviewer, desc(date)) %>%
  dplyr::distinct(id, Reviewer, .keep_all = T) %>%
  dplyr::select(1:5) %>%
  group_by(id) %>%
  add_count() %>%
  # dplyr::filter(n == 3) %>%  ## passed `consensus`
  dplyr::filter(n == 2) %>%    ## need `consensus`
  as.data.frame()

unique(dt_check$id)


dd1 <- dt_check %>%
  dplyr::distinct(id, Reviewer) %>%
  arrange(id, Reviewer) %>% 
  group_by(Reviewer) %>%
  summarise(id = str_c(id, collapse = ", ") )


dd2 <- aggregate(id ~ Reviewer, unique(dt_check), paste, collapse = ", ")
  
dd2
```


```{r - pre-processing }
dt_final <- dt %>%
  dplyr::rename("Magnitude" = "Was the `Flow Magnitude` quantified?") %>%
  ### - keep newest data and remove data in old dates
  # group_by(id, Reviewer) %>%
  arrange(id, Reviewer, desc(date)) %>%
  # dplyr::distinct(id, Reviewer, .keep_all = T) %>%
  ## - prioritize results by consensus 
  dplyr::distinct(id, .keep_all = T) %>%
  
  ## - remove text within parenthesis 
  dplyr::mutate(
    Levels = gsub("\\s*\\([^\\)]+\\)", "", Levels),
  ) %>%
  
  ## - remove unnecessary text 
  dplyr::mutate(
    Type = gsub("__ ", "", Type),
    Type = gsub("Other\\: ", "", Type),
    Levels = gsub("Other\\: ", "", Levels)) %>%
  as.data.frame()

# rm(d, dfs)


## manually fix this error
dt_final <- dt_final %>%
  dplyr::mutate(
     Levels = ifelse(id=='305' & Reviewer=='Xin Lan', 'International; National', Levels),
  )

names(dt_final)
```


```{r - check errors}
dt_err <- dt_final %>%
  # dplyr::filter(str_detect(Type, fixed('other', ignore_case = T))) %>%
  # dplyr::filter(str_detect(Type, fixed('Carbon', ignore_case = T))) %>% 
  # dplyr::filter(str_detect(Type, fixed('Virtual wood', ignore_case = T))) %>% # ''
  # dplyr::filter(str_detect(Type, fixed('Ecosystem services', ignore_case = T))) %>% 
  # dplyr::filter(str_detect(Type, fixed('Policies', ignore_case = T))) %>%               ## #267 by Nick
  # dplyr::filter(str_detect(Type, fixed('Cultural practices', ignore_case = T))) %>%     ## #93 by Nick
  # dplyr::filter(str_detect(Type, fixed('Seafood', ignore_case = T))) %>% ##
  # dplyr::filter(str_detect(Type, fixed('Nitrogen', ignore_case = T))) %>% ## Nitrogen
  # dplyr::filter(str_detect(Type, fixed('Urbanization', ignore_case = T))) %>%           ## Xiang
  # dplyr::filter(str_detect(Type, fixed('Ecological', ignore_case = T))) %>%             ## Ecological 
  # dplyr::filter(str_detect(Levels, fixed('ecoregion', ignore_case = T))) %>% 
  # dplyr::filter(str_detect(Levels, fixed('Internationl', ignore_case = T))) %>% ## 
  # dplyr::filter(is.na(`Data availability`)) %>%
  dplyr::filter(is.na(Magnitude)) %>%
  ## Policies
  as.data.frame()

# dt_err_ <- dt %>%
#   # dplyr::filter(id == '320') %>%
#   dplyr::filter(id == '134') %>%
#   dplyr::distinct(id, .keep_all = T) %>%
#   as.data.frame()
```


```{r - subset - water}
#' to see how many studies are on groundwater
#' 
subset_df <- dt_final %>%
  dplyr::mutate(Type = gsub('virtual water', '', Type)) %>%
  dplyr::filter(str_detect(Type, fixed('water', ignore_case=TRUE)))
```


```{r - To-do}
```
  
  * Revise and then send for consensus
  
  [x] #358 by Nan - "virtual wood products"
  [x] #51, #682 - missing input for "Data availability"
  [x] #134 - missing input for "Data availability"
  [x] deal with multiple coder's input, select whose? and select `Consensus`
  [x] Paper that coded by two coders, are need to be gone through `Consensus`
  [ ] Too many 'local' scales? - need to double-check
  
  




# Data cleaning 

```{r - functions}
expand_col_to_long <- function(data, target_col = "Mental health Types") {
  data_long <- data %>%
    dplyr::rename("col_split" = target_col) %>%
    cSplit(
      indt = .,
      splitCols = c("col_split"),
      sep = ";|,",
      drop = F, # drop the original col or not
      direction = "long", # this is better than "wide"
      stripWhite = T
    ) %>% # clean white space
    dplyr::mutate(across(where(is.factor), as.character)) %>%
    dplyr::mutate(col_split = trimws(col_split)) %>%

    ## capitalizes first word but not subsequent words
    dplyr::mutate(col_split = Hmisc::capitalize(col_split)) %>%
    as.data.frame() %>%
    # group_by(col_split) %>%
    # dplyr::summarise_at(c("n"), sum, na.rm = T) %>%
    as.data.frame()

  ## change back to the original column name
  names(data_long)[names(data_long) == "col_split"] <- target_col

  return(data_long)
}



plot_freq <- function(data, var = "Mental health Types") {
  p <- ggplot(
    data = data,
    aes(
      x = reorder(eval(parse(text = var)), n),
      y = n,
      # fill = n
  )) +
  geom_col() +
  theme_bw() +
  # theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  coord_flip() +
  # scale_fill_distiller(name = '', palette = "Blues", guide = "colorbar", direction = 1) +
  xlab("")
  
  return(p)
}


func_ggsave <- function(fname, w = 7, h = 5) {
  ggsave(filename = fname, plot = last_plot(), width = w, height = h, units = "in", dpi = 300)
}
```


```{r - Type, include=FALSE}
## keep columns of interest, and clean data

type_top_colors <- c('#1f78b4','#a6cee3','#b2df8a')
type_top_levels <- c('Physical Flows', 'Non-material Flows', 'Virtual Flows')
org_levels <- c("International", "National", "Subnational", "Local")


## stat
## - by Type
dt.type <- dt_final %>%
  group_by(Type, Levels, `Data availability`) %>%
  dplyr::count() %>%
  ungroup() %>%
  as.data.frame()

physical_flow_list <- c(
  'raw materials', 'goods and products', 'energy', 'water', 'pollutants/waste', 'animal migration',
  'species dispersal', 'disease transmission', 'people',
  'sediment'
) %>%
  Hmisc::capitalize(.)
  

## - clean and format
dt.type.cl <- dt.type %>%
  dplyr::mutate(
    Type = gsub("\\(e\\.g\\., land grab, land acquisition, land requisition\\)", "", Type),
    
    ) %>%
  expand_col_to_long(data = ., target_col = "Type") %>%
  dplyr::filter(Type != 'Physical Flows') %>%
  ## clear text and add top category 
  dplyr::mutate(
    
    Type = trimws(Type),
    
    ## fix manual input values
    Type = ifelse(Type %in% c('Animals (trade)', 'Animals (pandas)', 'Animals (illegal trade)',
                              'Wildlife trade'), 
                  'goods and products', Type),
    
    Type = ifelse(Type %in% c('Land requisition'), 'transfer ownership and use of land', Type),
    Type = ifelse(Type %in% c('Virtual nitrogen', 'Virtual phosphorus'), 'Virtual N/P', Type),
    Type = ifelse(Type %in% c('Ecological footprints'), 'Virtual land', Type), # 
    Type = ifelse(Type %in% c('Seafood footprint', 'Virtual energy'), 'Virtual EF (other)', Type),
    Type = Hmisc::capitalize(Type),
    Type = ifelse(Type %in% c('Carbon', 'Nitrogen'), 'Pollutants/waste', Type),
    
    type_top = case_when(
      str_detect(Type, regex('virtual|footprint', ignore_case=TRUE)) ~ 'Virtual Flows',
      Type %in% physical_flow_list ~ 'Physical Flows',
      TRUE ~ 'Non-material Flows'),
    type_top = factor(type_top, levels = type_top_levels),
    
    
    ## rename flows
    Type = ifelse(Type %in% c('Cultural ecosystem services'), 'Cultural ES', Type),
    Type = ifelse(Type %in% c('Goods and products', 'Energy'), 'Trade of goods', Type),
    Type = gsub('raw materials', 'Trade of raw materials', Type, ignore.case=TRUE),
    Type = ifelse(Type %in% c('Financial/investments'), 'Financial', Type),
    Type = ifelse(Type %in% c('People'), 'Human', Type),
    Type = ifelse(Type %in% c('Sediment'), 'Water', Type),
    Type = ifelse(Type %in% c('Transfer ownership and use of land'), 'Land deals', Type),
    Type = ifelse(Type %in% c('Technology', 'Knowledge', 'Land deals'), 'Information', Type),
    Type = ifelse(Type %in% c('Virtual GHG emissions'), 'Virtual emissions', Type), 
    Type = ifelse(Type %in% c('Social footprints/risks'), 'Virtual SF', Type),
    Type = ifelse(Type %in% c('Pollutants/waste'), 'Pollutants', Type),
    
  ) %>%
  dplyr::filter(!Type %in% c(
    'Other', 
    'Virtual wood products trade', 
    'Policies',
    'Cultural practices',
    'Ecosystem services' ## overlapped with other input
    )) %>%
  as.data.frame()
  
  
dt.type.clean <- dt.type.cl  %>%
  group_by(Type, type_top) %>%
  dplyr::summarise_at(c("n"), sum, na.rm = T) %>%
  ungroup() %>%
  dplyr::mutate(total = sum(n, na.rm = T),
                percent = round(n/total*100, digits = 0),
                percent_lab = paste0(percent, '%')
                ) %>%
  arrange(type_top) %>%
  as.data.frame()
```


```{r - Type - bar}
dt.type.clean %>%
  # dplyr::slice_max(order_by = n, n = 20) %>%
  ggplot(aes(
    x = reorder(Type, n),
    y = n,
    fill = type_top
  )) +
  geom_col() +
  geom_text(
    # aes(label = ifelse(as.numeric(percent) >= 5, percent_lab, NA)), 
    aes(label = percent_lab), 
    vjust = 0.5, 
    hjust = -0.1
  ) +
  ylim(0, 185) +
  xlab("") +
  ylab("Number of studies") +
  coord_flip() +
  # scale_fill_distiller(name = '', palette = "Blues", guide = "colorbar", direction = 1) +
  scale_fill_manual(values = type_top_colors, name = 'Categories') +
  # ggtitle("Frequency of Flow Types") +
  theme_bw() +
  theme(
    panel.grid = element_line(size = 0.2),
    panel.grid.minor = element_blank(),
    # axis.text.x = element_text(angle = 45, vjust = 1, hjust=1), 
    axis.title.y = element_blank(),
    legend.position = c(0.8, 0.15)
    )

fname <- paste0(dir.fig, "flow_types.png")
func_ggsave(fname = fname)
```



```{r - Magnitude}
dt.m <- dt_final %>%
  ### - stat
  group_by(Magnitude) %>%
  dplyr::tally() %>%
  ungroup() %>%
  dplyr::filter(Magnitude != 'NA') %>% ## 4 of which have missing input
  dplyr::mutate(total = sum(n, na.rm = T),
                percent = n/total*100) %>%
  as.data.frame()
```


```{r - Direction}
dt.dir <- dt_final %>%
  ### - stat
  group_by(`Flow Directions`) %>%
  dplyr::tally() %>%
  ungroup() %>%
  dplyr::filter(`Flow Directions` != 'NA') %>% ## 1 of which have missing input
  dplyr::mutate(total = sum(n, na.rm = T),
                percent = n/total*100) %>%
  as.data.frame()
```


```{r - Distance}
dt.dis <- dt_final %>%
  ### - stat
  dplyr::rename("Distance" = "Flow Distance") %>%
  ## clear text and add top category ----------------
  dplyr::mutate(
    Distance = gsub("Other\\: ", "", Distance),
    Distance = gsub("&", ";", Distance),
    Distance = trimws(Distance),
    Distance = Hmisc::capitalize(Distance),
  ) %>%
  expand_col_to_long(data = ., target_col = "Distance") %>%
  group_by(Distance) %>%
  dplyr::tally() %>%
  ungroup() %>%
  # dplyr::filter(Directions != 'NA') %>% ## 1 of which have missing input
  dplyr::mutate(total = sum(n, na.rm = T),
                percent = n/total*100) %>%
  as.data.frame()
```



```{r - Mode}
dt.mod <- dt_final %>%
  ### - stat
  dplyr::rename("Mode" = "Flow Mode") %>%
  ## clear text and add top category ----------------
  dplyr::mutate(
    Mode = gsub("Other\\: ", "", Mode),
    Mode = gsub('Carbon flow via tourism', "Active movement of people and animals", Mode, ignore.case = T), # 
    Mode = gsub('Financial/Capital flows through banking or debt|Spatial subsidy values', "Financial flow", Mode, ignore.case = T),
    Mode = gsub('Virtual water use', "Trade-related flows via Man-made carriers", Mode, ignore.case = T),
    Mode = gsub('Ecosystem services flow', "Biophysical flow through ecological processes", Mode, ignore.case = T),# 
    Mode = trimws(Mode),
    Mode = Hmisc::capitalize(Mode),
  ) %>%
  expand_col_to_long(data = ., target_col = "Mode") %>%
  group_by(Mode) %>%
  dplyr::tally() %>%
  ungroup() %>%
  # dplyr::filter(Directions != 'NA') %>% ## 1 of which have missing input
  dplyr::mutate(total = sum(n, na.rm = T),
                percent = n/total*100) %>%
  arrange(desc(percent)) %>%
  as.data.frame()
```


```{r - Levels, include=FALSE}
## - by scale
dt.bylevel <- dt_final %>%
  ### -clean up the names of the tools
  # dplyr::select(1:5, Levels, -Title) %>%
  # dplyr::filter(nchar(Levels) < 180) %>%
  # dplyr::filter(str_detect(string = Levels, pattern = "exclude", negate = T)) %>%
  # dplyr::mutate(
  #   Tool = gsub("scales|Scales", "scale", Levels),
  #   Tool = gsub("\\s*\\([^\\)]+\\)", "", Tool)) %>% ## remove any strings in a ()
  
  ### - stat
  group_by(Levels, `Data availability`) %>%
  dplyr::count() %>%
  ungroup() %>%
  dplyr::filter(Levels != 'NA') %>%
  as.data.frame()



func_clean_levels <- function(data, target_col = "Levels") {
  
  dd <- expand_col_to_long(data = data, target_col = "Levels") %>%
  
  ## clear text and add top category ----------------
  dplyr::mutate(
    Levels = gsub('and|And|\\.|\\-', '', Levels),
    Levels = gsub('internationl|Internationl', 'International', Levels),
    Levels = trimws(Levels),
    Levels = Hmisc::capitalize(Levels),
  ) %>%
  dplyr::filter(!Levels %in% c(
    'Biome', 'Ecoregion', 'River basin', 'Other:'
    )) %>%
  as.data.frame()
  
  return(dd)
  
}


dt.bylevel.cl <- dt.bylevel %>%
  func_clean_levels(data = .) %>%
  group_by(Levels, `Data availability`) %>%
  dplyr::summarise_at(c("n"), sum, na.rm = T) %>%
  as.data.frame()
  
unique(dt.bylevel.cl$Levels)
unique(dt.bylevel.cl$`Data availability`)
  
dt.bylevel.clean <- dt.bylevel.cl  %>%
  dplyr::mutate(
    Levels = factor(Levels, levels = org_levels),
    `Data availability` = factor(`Data availability`, levels = c("Low", "Moderate", "High")),
    ) %>%
  as.data.frame()

# dt.bylevel.clean$Levels <- factor(x = dt.bylevel.clean$Levels, levels = org_levels)
levels(dt.bylevel.clean$Levels)
```



```{r - Level - bar}
dt.bylevel.clean %>%
  # dplyr::slice_max(order_by = n, n = 20) %>%
  # plot_freq(data = ., var = 'Levels') +
  ggplot(aes(
    x = reorder(Levels, n),
    y = n,
    fill = `Data availability`
  )) +
  # geom_col() +
  geom_bar(position="stack", stat="identity", width = .8, linewidth = .1, color = 'gray90') +
  scale_fill_brewer(palette = 'Greys', direction = 1) +
  coord_flip() +
  # xlab("") +
  ylab("Number of studies") +
  # ggtitle("Frequency of Organizational levels") +
  theme_bw() +
  theme(
    legend.position = c(0.85, 0.15), 
    axis.title.y = element_blank(),
    )

fname <- paste0(dir.fig, "flow_org_levels.png")
func_ggsave(fname = fname)
```




```{r - Type + Levels + availability}
dt.type.cl1 <- dt.type.cl  %>%
  # expand_col_to_long(data = ., target_col = "Levels") %>%
  func_clean_levels(data = .) %>%
  group_by(type_top, Type, Levels, `Data availability`) %>%
  dplyr::summarise_at(c("n"), sum, na.rm = T) %>%
  # arrange(type_top) %>%
  dplyr::mutate(
    # `Data availability` = ifelse(`Data availability` == 'Moderate', 'High', `Data availability`),
    `Data availability` = case_when(
      `Data availability` == 'High'     ~ '+++',
      `Data availability` == 'Moderate' ~ '++',
      `Data availability` == 'Low'      ~ '+', 
      T ~ `Data availability`),
    Levels = paste0(Levels, '\n(', `Data availability`, ')'),
    id = row_number()) 


dt.type.cl2 <- dt.type.cl1 %>%
  pivot_longer(names_to = 'dimension', 
               values_to = 'layers', 
               cols = c('type_top', 'Type', 'Levels')) %>% # , 'Data availability'
  group_by(dimension) %>%
  dplyr::mutate(id_within_layers = row_number(dimension)) %>%
  arrange(dimension) %>%
  dplyr::rename(freq = n) %>%
  dplyr::mutate(
    dimension = factor(
      dimension, 
      levels = c('type_top', 'Type', 'Levels'), # , 'Data availability'
      labels = c('Flow type categories', 'Flow examples', 'Levels (Data availability)')), # , 'Data availability'
    # layers = factor(layers, levels = org_levels)
    ) %>%
  group_by(layers) %>%
  dplyr::mutate(total = sum(freq, na.rm = T)) %>%
  as.data.frame()
  


str(dt.type.cl2)

dt.type.clean_sort <- dt.type.clean %>%
  group_by(type_top) %>%
  arrange(type_top, n)
str(dt.type.clean)
dt.type.clean_sort$Type

sort_by <- c(dt.type.clean_sort$Type, levels(dt.type.clean_sort$type_top), org_levels)
  
dt.type.cl3 <- dt.type.cl2 %>%
  dplyr::mutate(
    layers = factor(layers, levels = sort_by),
    )


library(RColorBrewer)
colourCount = length(unique(dt.type.cl2$layers))
getPalette = colorRampPalette(brewer.pal(12, "Paired"))
 
packageVersion('ggrepel')

library(ggalluvial)
width_my <- 1/2.5
y_max <- sum(dt.type.cl2$freq)/3

sorted <- T  ## sorted by flow size
sorted <- NA ## default setting, sorted alphabetically 

func_alluvial <- function(data, 
                          sorted = NA,
                          # indicator_n_min = 5, 
                          width_my = 1/2.5, 
                          # w_p = 6,
                          labele_small = 10,
                          n_ctr = '',
                          filename.postfix = '') {
  p <- data  %>%
    ggplot(.,
         aes(x = dimension, 
             y = freq,
             alluvium = id_within_layers, 
             stratum = layers, 
             fill = layers)) +
    scale_x_discrete(expand = c(.1, 0)) +
    # scale_fill_manual(values = getPalette(colourCount)) +
    # geom_flow(width = width_my) +
    geom_flow(width = width_my,
              # aes.bind = TRUE,
              decreasing = sorted) +
    geom_stratum(alpha = .6, width = width_my, 
                 decreasing = sorted) +
    stat_stratum(geom = "text",
                 aes(label = ifelse(as.numeric(total) >= labele_small, layers, NA)),
                 decreasing = sorted) +
    
    # geom_text(stat = "stratum", check_overlap = T,
              # label = after_stat(stratum),
    #           # aes(label = paste0(stratum,
    #           #                    ifelse(nchar(as.character(stratum)) == 1L,
    #           #                           ": ", "\n"),
    #           #                    after_stat(n)))
    #           ) +
    
    # annotate(
    #   geom = "curve", x = 1, y = y_max, xend = 1.1, yend = y_max+20, 
    #   curvature = .3, arrow = arrow(length = unit(1, "mm"))
    # ) +
    # annotate(geom = "text", x = 1.11, y = y_max+20, label = "Virtual SF", hjust = "left", size=3) +
    
    ggrepel::geom_text_repel(
      decreasing = sorted,
      aes(label = ifelse(as.numeric(total) < labele_small, as.character(layers), NA) ),
      # segment.square  = F,
      # segment.inflect = T,
      segment.size    = 0.3,
      segment.alpha   = .7,
      segment.curvature = 0.2, ## negative for left-hand and positive for right-hand curves, 0 for straight lines
      # segment.curvature = -1e-20,
      segment.ncp = 3,
      segment.angle = 20, ## values greater than 90 would skew toward the end
      
      nudge_x = .4,
      nudge_y = .5,
      
      # point.padding = unit(30, "mm"),
      force_pull = 1,
      direction = 'both',
      # direction = "y",
      
      # arrow = arrow(length = unit(1, "mm")),
      
      stat = "stratum",
      size = 3
    ) +
  
  
    theme_classic() +
    theme(legend.position = "none",
          axis.title  = element_blank(),
          axis.line = element_blank(),
          # axis.ticks.x = element_blank(),
          axis.ticks  = element_blank(),
          axis.text.y =  element_blank(),
          axis.text.x = element_text(size=rel(1.4), 
                                     vjust = 10,
                                     margin = margin(t = 0, r = 0, b = 0, l = 0)))
  
  return(p)
}



func_alluvial(data = dt.type.cl2, sorted = NA)
getwd()
f <- paste0('FlowType_scale_pairs', today, '-6.png')
fname <- paste0(dir.fig, f); fname
ggsave(filename = fname, plot = last_plot(), width = 11, height = 9, units = 'in', dpi = 300)

```


  * This plot will be used to PS the above figure, so that the flows can be sent from the axis in the middle to the two sides (i.e., axis of Categories, and axis of Levels)
```{r --- flow cat - type}
dtt1 <- dt.type.cl1 %>%
  pivot_longer(names_to = 'dimension', 
               values_to = 'layers', 
               cols = c('type_top', 'Type', 'Levels')) %>% # , 'Data availability'
  group_by(dimension) %>%
  dplyr::mutate(id_within_layers = row_number(dimension)) %>%
  arrange(dimension) %>%
  dplyr::rename(freq = n) %>%
  dplyr::mutate(
    dimension = factor(
      dimension, 
      levels = c('Type', 'type_top', 'Levels'), # , 'Data availability'
      labels = c('Flow examples', 'Flow type categories', 'Levels (Data availability)')), # , 'Data availability'
    # layers = factor(layers, levels = org_levels)
    ) %>%
  group_by(layers) %>%
  dplyr::mutate(total = sum(freq, na.rm = T)) %>%
  as.data.frame()
  

func_alluvial(data = dtt1, sorted = NA, labele_small = 1)
f <- paste0('FlowType_scale_pairs', today, '-6.1.png')
fname <- paste0(dir.fig, f); fname
ggsave(filename = fname, plot = last_plot(), width = 11, height = 9, units = 'in', dpi = 300)
```



```{r - test 1, eval=FALSE, include=FALSE}
aes.bind_my <- "flows"
# aes.bind_my <- "alluvia"

dt.type.cl2 %>%
  ggplot(.,
       aes(x = dimension, 
           y = freq,
           alluvium = id_within_layers, 
           stratum = layers, 
           fill = layers, 
           label = layers)) +
  scale_x_discrete(expand = c(.1, 0)) +
  geom_flow(width = width_my) +
  
  # geom_flow(width = width_my,
  #           decreasing = TRUE) +
  
  stat_alluvium(aes.bind = aes.bind_my) +
  # geom_stratum(alpha = .5, width = width_my, 
  #              decreasing = TRUE) +
  stat_stratum() +
  stat_stratum(geom = "text") +
  stat_alluvium(geom = "text", 
                aes.bind = aes.bind_my) +
  theme_classic() +
  theme(legend.position = "none",
        axis.title  = element_blank(),
        axis.line = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_text(size=rel(1.4), 
                                   vjust = 10,
                                   margin = margin(t = 0, r = 0, b = 0, l = 0)))

f <- paste0('FlowType_scale_pairs_', aes.bind_my, '.png')
fname <- paste0(dir.fig, f); fname
# ggsave(filename = fname, plot = last_plot(), width = 16/1.5, height = 10, units = 'in', dpi = 300)
```



```{r - test 2, eval=FALSE, include=FALSE}
dt.type.cl3 %>%
  ggplot(.,
       aes(x = dimension, 
           y = freq,
           alluvium = id_within_layers, 
           stratum = layers, 
           fill = layers, 
           label = layers)) +
  scale_x_discrete(expand = c(.1, 0)) +
  geom_flow(width = width_my) +
  geom_stratum(alpha = .5, width = width_my) +
  stat_stratum(geom = "text") +
  theme_classic() +
  theme(legend.position = "none",
        axis.title  = element_blank(),
        axis.line = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_text(size=rel(1.4), 
                                   vjust = 10,
                                   margin = margin(t = 0, r = 0, b = 0, l = 0)))


getwd()
f <- 'FlowType_scale_pairs0.png'
fname <- paste0(dir.fig, f); fname
ggsave(filename = fname, plot = last_plot(), width = 16/1.5, height = 10, units = 'in', dpi = 300)
```








